Efficient Calculation of Polynomial and Interaction Features on Sparse Matrices

### 2015-10-05 paper/paper2.tex
resized boundaries image to not cut off text
cleaned up conclusion

\begin{sidewaysfigure}
    \centering
    \includegraphics[scale=0.3]{boundaries.eps}

@@

This work also gives a general pattern for calculating polynomial features of arbitrary degrees:
instead of finding a mapping from the 2-tuples of indices onto the space $\{0, 1, ..., \frac{D^2+D}{2}-1\}$,
construct a mapping from k-tuples of indices onto the space $\{0, 1, ..., \binom{D+k-1}{D-1}-1\}$, where $k$ is the degree of the polynomial.
In terms of the upper triangular matrix analogy, this corresponds with mapping the upper k-simplex of a $(D, D, ..., D)$-tensor onto
the space $\{0, 1, ..., \binom{D+k-1}{D-1}-1\}$. For the average case of $dD$ nonzero elements per row, 
there will be $\binom{dD+k-1}{dD-1} = $ polynomial features, so the average time complexity for an $N \times D$ matrix
is $\Theta(Nd^kD^k)$, which means that its time complexity polynomially decreases with respect to the density
compared to the dense algorithm (which has $O(ND^k)$ and $\Theta(ND^k)$).

>>>>

\begin{sidewaysfigure}
    \centering
    \includegraphics[scale=0.25]{boundaries.eps}

@@

This work also gives a general pattern for calculating polynomial features of arbitrary degrees:
instead of finding a mapping from the 2-tuples of indices onto the space $\{0, 1, ..., \frac{D^2+D}{2}-1\}$,
construct a mapping from k-tuples of indices onto the space $\{0, 1, ..., \binom{D+k-1}{D-1}-1\}$, where $k$ is the degree of the polynomial.
In terms of the upper triangular matrix analogy, this corresponds with mapping the upper k-simplex of a $(D, D, ..., D)$-tensor onto
the space $\{0, 1, ..., \binom{D+k-1}{D-1}-1\}$. For the average case of $dD$ nonzero elements per row, 
there will be $\binom{dD+k-1}{dD-1}$ polynomial features, so the average time complexity for an $N \times D$ matrix
is $\Theta(Nd^kD^k)$, which means that its time complexity polynomially decreases with respect to the density
compared to the dense algorithm (which has $O(ND^k)$ and $\Theta(ND^k)$).
